Implementing Real-time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
Adds Transport Service and Return Value to API table

\documentclass{sig-alternate-05-2015}
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}       
\usepackage[british]{babel}        
\usepackage[babel=true]{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{bytefield}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage{balance}

@@

\begin{table}
  \centering
  \begin{tabular}{ll}
    \toprule
      Function & Parameters \\
    \midrule
      \texttt{socket} & \texttt{af} -- Address family \\
                      & \texttt{st} -- Socket type \\
      \texttt{close} & \texttt{sd} -- Socket descriptor \\
    \midrule
      \texttt{bind} & \texttt{sd} -- Socket descriptor \\
                    & \texttt{addr} -- Address to bind to \\
                    & \texttt{addrlen} -- Length of \texttt{addr} \\
      \texttt{listen} & \texttt{sd} -- Socket descriptor \\
            \texttt{accept} & \texttt{sd} -- Socket descriptor \\
                    & \texttt{addr} -- Address of peer \\
                    & \texttt{addrlen} -- Length of \texttt{addr} \\
      \texttt{connect} & \texttt{addr} -- Address to connect to \\
                    & \texttt{addrlen} -- Length of \texttt{addr} \\
    \midrule
      \texttt{set\_po\_delay} & \texttt{delay} -- Playout delay (in ms) \\
    \midrule
      \texttt{send\_message} & \texttt{sd} -- Socket descriptor \\
      & \texttt{buf} -- Message data \\
      & \texttt{len} -- Length of message data \\
      & \texttt{seq\_num} -- Sequence number \\
      & \texttt{deadline} -- Relative deadline of message (in ms) \\ 
      & \texttt{depends\_on} -- \texttt{seq\_num} of dependency \\
      & \texttt{substream} -- Substream identifier \\
      \texttt{recv\_message} & \texttt{sd} -- Socket descriptor \\
      & \texttt{buf} -- Buffer for message data \\
      & \texttt{len} -- Size of \texttt{buf} \\
      & \texttt{substream} -- Substream identifier \\
      & \todo{return value, rather than param?}\\
    \bottomrule
  \end{tabular}
  \caption{Outline transport API for real-time applications 
          \todo{show return values of these calls}}
  \label{tab:api}
\end{table}

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}       
\usepackage[british]{babel}        
\usepackage[babel=true]{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{bytefield}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage{balance}
\usepackage{tabularx}

@@

\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{llll}
    \toprule
      Transport Service            & Function & Parameters                                     & Return Value \\
    \midrule
                                   & \texttt{socket}         
                                              & \texttt{af} -- Address family                  & Socket descriptor \\
                                   &          & \texttt{st} -- Socket type & \\
                                   & \texttt{close}          
                                              & \texttt{sd} -- Socket descriptor               & 0 (success), -1 (error) \\
    \midrule
      \textbf{Connection oriented} & \texttt{bind}           
                                              & \texttt{sd} -- Socket descriptor               & 0 (success), -1 (error) \\
                                   &          & \texttt{addr} -- Address to bind to & \\
                                   &          & \texttt{addrlen} -- Length of \texttt{addr} & \\
                                   & \texttt{listen}         
                                              & \texttt{sd} -- Socket descriptor               & 0 (success), -1 (error) \\
                                   & \texttt{accept}        
                                              & \texttt{sd} -- Listening socket descriptor     & Connection socket descriptor \\
                                   &          & \texttt{addr} -- Address of peer & \\
                                   &          & \texttt{addrlen} -- Length of \texttt{addr} & \\
                                   & \texttt{connect}        
                                              & \texttt{addr} -- Address to connect to         & 0 (success), -1 (error) \\
                                   &          & \texttt{addrlen} -- Length of \texttt{addr} & \\
    \midrule
      \textbf{Deadlines}           & \texttt{set\_po\_delay} 
                                              & \texttt{delay} -- Playout delay (in ms)        & 0 (success), -1 (error) \\
    \midrule
      \textbf{Message oriented}    & \texttt{send\_message}  
                                              & \texttt{sd} -- Socket descriptor               & Number of bytes sent \\
                                   &          & \texttt{buf} -- Message data & \\
                                   &          & \texttt{len} -- Length of message data & \\
                                   &          & \texttt{seq\_num} -- Sequence number & \\
      \emph{Deadlines}             &          & \texttt{deadline} -- Relative deadline of message (in ms) & \\ 
      \emph{Dependencies}          &          & \texttt{depends\_on} -- \texttt{seq\_num} of dependency & \\
      \emph{Sub-streams}           &          & \texttt{substream} -- Substream identifier & \\
                                   & \texttt{recv\_message}  
                                              & \texttt{sd} -- Socket descriptor               & Number of bytes received \\
                                   &          & \texttt{buf} -- Buffer for message data & \\
                                   &          & \texttt{len} -- Size of \texttt{buf} & \\
      \emph{Sub-streams}           &          & \texttt{substream} -- Substream identifier & \\
                                   &          & \todo{return value, rather than param?} & \\
    \bottomrule
  \end{tabularx}
  \caption{Outline transport API for real-time applications. Return values
  shown are for successful calls; in all cases, -1 is returned in the event
  of an error}
  \label{tab:api}
\end{table*}
